Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems

### 2017-11-21 LaTeX/Turnover.tex
need to check invasion regions are real with invasionplotXY

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive_Mike}}
\caption{
Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined. 
In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=0.6$, $w_{AA}^\female=0.6$).
%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
}
\label{fig:regionMaleDrive}
\end{figure}

\newpage
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS_Mike}}
\caption{
Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex-ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B). 
}
\label{fig:regionMaleGS}
\end{figure}

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
\caption{
Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
}
\label{fig:regionFemaleDrive}
\end{figure}

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS_Mike}}
\caption{
Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
The $a$ allele is favoured during female gametic competition in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
The $A$ allele is favoured during gametic competition in panels D-F ($\alpha_{\Delta}^\female=-0.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
}
\label{fig:regionFemaleGS}
\end{figure}

>>>>

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
\caption{
Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined. 
In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
}
\label{fig:regionMaleDrive}
\end{figure}

\newpage
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
\caption{
Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex-ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B). 
}
\label{fig:regionMaleGS}
\end{figure}

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
\caption{
Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
}
\label{fig:regionFemaleDrive}
\end{figure}

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
\caption{
Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
}
\label{fig:regionFemaleGS}
\end{figure}
